\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-13 article.tex
elaborate spilling heuristic

\subsection{Heuristics spilling}
\usetikzlibrary{chains,arrows}
\begin{figure}[H]
    \centering
    \begin{minipage}[b]{0.31\textwidth}
      \centering
      \begin{tikzpicture}[scale=0.4]
        \node[above] at (0,0) {\texttt{\%3}};
        \node[above] at (1,-1) {\texttt{\%4}};
        \node[above] at (2,-2) {\texttt{\%5}};
        \node[above] at (3,-4) {\texttt{\%7}};
        \node[above] at (4,-5) {\texttt{\%8}};
        \draw[|-|] (0,0) edge   (0,-3);
        \draw[|-|] (1,-1) edge   (1,-5);
        \draw[|-|] (2,-2) edge   (2,-8);
        \draw[|-|] (3,-4) edge   (3,-7);
        \draw[|-|] (4,-5) edge   (4,-6);

>>>>

\subsection{Spilling heuristics}
The spilling heuristic can vary, but the one mentioned in the paper is chosen from remaining length, as in  \textit{\textquoteleft furthest away from the current point\textquoteright} \cite[900]{linear}. The same decision was made for this implementation, as it does stand to reduce the amount of spills necessary. See The program of Figure \ref{fig:linear.ll} and its associated live ranges/intervals of Figure \ref{fig:linear.lra}. For a target of \(k=2\), upon reaching the start of interval \texttt{\%5},  one variable needs to be spilled. If either \texttt{\%3} or \texttt{\%4} are chosen, in the case of \texttt{\%3} being spilled, already upon reaching \texttt{\%7} another needs to be spilled. In case of \texttt{\%4}, two variables won't be live simultaneously until \texttt{\%8}. Nonetheless, that means two spills instead of spilling the longest interval of \texttt{\%5}.
\usetikzlibrary{chains,arrows}
\begin{figure}[H]
    \centering
    \begin{minipage}[b]{0.31\textwidth}
      \centering
      \begin{tikzpicture}[scale=0.4]
        \node[above] at (0,0) {\texttt{\%3}};
        \node[above] at (1,-1) {\texttt{\%4}};
        \node[above] at (2,-2) {\texttt{\%5}};
        \node[above] at (3,-4) {\texttt{\%7}};
        \node[above] at (4,-5) {\texttt{\%8}};
        \draw[|-|] (0,0) edge   (0,-3);
        \draw[|-|] (1,-1) edge   (1,-5);
        \draw[|-|] (2,-2) edge   (2,-8);
        \draw[|-|] (3,-4) edge   (3,-7);
        \draw[|-|] (4,-5) edge   (4,-6);
